Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-11 paper.tex
Replace Fig: homogeneous absorption star

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-absorption_sphere}
  \caption{Distribution function outside a constant-density star
    with radius $R=15$~km, and observer at $r=22.5$~km.
    $A$ is the angle between the neutrino momentum and the $\hat{r}$ direction.
    The sample grid uses 30 points in energy and angle spanning the ranges
    $\varepsilon\in(0,100)$~MeV and $\cos A\in(0.6454,1)$,
    with sample points at bin centers.
    The line depicts the analytic result for one energy: $\varepsilon=15$~MeV.
    Test described in Sec.~\ref{ssec:test_ab_star}}
  \label{fig:f_absorption_sphere}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-f-absorption_star-11MeV}
  \caption{Distribution functions outside an idealized homogeneous star
    with radius $R=50$~km, and observer at $r=75$~km.
    $A$ is the angle between the neutrino momentum and the $\hat{r}$ direction.
    The sample grid uses 40 points in energy linearly spaced across
    $\varepsilon\in(0,100)$~MeV,
    and 30 points in cosine of the polar angle linearly spaced across
    $\cos A\in(0.7377,1)$.
    To simplify this plot a single energy group only is displayed:
    $\varepsilon=11.25\,{\rm MeV}$.
    The points are computed from ray tracing; the lines from the analytic
    solution.
    Test described in Sec.~\ref{ssec:test_ab_star}.
  }
  \label{fig:f_absorption_sphere}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-G_spectra-absorption_star}
  \caption{Number density spectra for an idealized homogeneous star.
    Test described in Sec.~\ref{ssec:test_ab_star}.
    The lines with points are the ray tracing spectra for this configuration;
    the solid lines are the ray tracincg spectra for an otherwise identical star
    of infinite extent (i.e. the spectra from Sec.~\ref{ssec:test_equilibrium}).
  }
  \label{fig:G_absorption_sphere}
\end{figure}
